The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-03 paper.tex
update

\begin{document}
\title{The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study}

@@

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two large bubbles symmetrically extending about 50 degrees above and below the Galactic center,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

@@

Over the course of a decade,\
the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a giant hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
symmetrically extending about 80 degress above and below GC.

The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and has remarkable morphological symmetry about the Galactic plane as the Fermi bubbles.

@@

Early attempts to model the Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)\
assumed that the jet is vertial to the Galactic plane...

@@

\subsection{Inclined jet injection}
  Early observation \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  A number of galaxies in which the jets are tilted to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

>>>>

\begin{document}
\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}

@@

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

@@

Over the course of a decade,\
the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a giant hourglass-shaped structure (eROSITA bubbles hereafter) at the GC,\
but extending about twice as large as the Fermi bubbles.

The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and displays morphological symmetry about the Galactic plane as the Fermi bubbles.

@@

Early attempts to model the Fermi and eROSITA bubbles (collectiely we call the Galactic bubbles)\
assumed that the jet is vertial to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to the plane of the disc.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

To this end, this work consider a dense thin disk of interstellar medium\
around a jet source, in an attempt to remedy the symmetry problem of the Galactic bubbles.\

We perform three-dimensional special relativistic hydrodynamics simulations\
of the formation of the Galactic bubbles by CR jet injections\
from the central SMBH in the Galaxy.

This paper is organized as follows. We introduce

@@

\subsection{Inclined jet injection}
